---
title: "link-card"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{link-card}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(grkgdown)
```

## Simple Cards

```{=html}
<div class="d-grid" style="grid-template-columns: repeat(auto-fill, minmax(325px, 1fr)); gap: 1em;">
<!-- card -->
<div class="card card-as-link">
<div class="card-body">
<h3 class="card-title mt-0 mb-3"><a href="../reference/index.html" class="card-primary-link card-header-link text-decoration-none">Reference</a></h3>
<p class="card-text">Something about the detailed docs or API reference.</p>
</div>
</div>
<!-- /card -->
<!-- card -->
<div class="card card-as-link">
<div class="card-body">
<h3 class="card-title mt-0 mb-3"><a href="../index.html" class="card-primary-link card-header-link text-decoration-none">Home</a></h3>
<p class="card-text">Get up and running with a pkgdown template package.</p>
</div>
</div>
<!-- /card -->
</div>
```

### Card Markup

Use a raw html block with a grid (`class="d-grid"`). I've used

```css
grid-template-columns: repeat(auto-fill, minmax(325px, 1fr))
gap: 1em;
```

as inline styles to get decent behavior across all screen sizes.

````{verbatim}
```{=html}
<div class="d-grid" style="grid-template-columns: repeat(auto-fill, minmax(325px, 1fr)); gap: 1em;">
<!-- cards -->
</div>
```
````

Card markup is as follows. Give the card container `card-as-link` class. And ensure that there is one link with the class `card-primary-link`. If this link is in a header element, also give it `card-header-link`, othewise this could also be a right-aligned button at the end of the card.

```html
<!-- card -->
<div class="card card-as-link">
<div class="card-body">
<h3 class="card-title mt-0 mb-3">
<a href="../index.html" class="card-primary-link card-header-link text-decoration-none">Home</a>
</h3>
<p class="card-text">Get up and running with a pkgdown template package.</p>
</div>
</div>
<!-- /card -->
```

## Complex Cards

```{=html}
<div class="d-grid" style="grid-template-columns: repeat(auto-fill, minmax(325px, 1fr)); gap: 1em;">
<div class="card card-as-link">
<img src="https://source.unsplash.com/aTKJ22OrbrU" class="card-img-top" alt="">
<div class="card-body">
<h3 class="card-title mt-0 mb-3">grkgdown</h3>
</h3>
<p class="card-text">Get up and running with a pkgdown template package.</p>
<a href="../index.html" class="btn btn-primary float-end card-primary-link">Package Home</a>
</div>
</div>
</div>
```

### Markup

```html
<div class="d-grid" style="grid-template-columns: repeat(auto-fill, minmax(325px, 1fr)); gap: 1em;">
<!-- card -->
<div class="card card-as-link">
<img src="https://source.unsplash.com/aTKJ22OrbrU" class="card-img-top" alt="">
<div class="card-body">
<h3 class="card-title mt-0 mb-3">grkgdown</h3>
</h3>
<p class="card-text">Get up and running with a pkgdown template package.</p>
<a href="../index.html" class="btn btn-primary float-end card-primary-link">Package Home</a>
</div>
</div>
<!-- /card -->
</div>
```
